I would like to thank my supervisor, Prof. Dr. Weber-Wulff, for her guidance throughout this thesis. \\

I am very grateful for the opportunity to have worked with Lydia Pintscher over the last year. She was my mentor and became a great inspiration. \\

On a technical level, Marius Hoch supported me whenever necessary. Late night core patches to help my project continue are just one of many reasons I am very thankful to have the opportunity to work with him. He introduced me to the wonders and frustrations of working on a big and amazing open source project. Without him, this project would barely have been at the stage it is now. \\

The Wikidata team has helped and supported me patiently over the last year and while writing the thesis. Code review, patches, advice---I am very thankful to work with them: Daniel Kinzler, Katie Filbert, Marius, Adam Shorland, Jan Zerebecki, Adrian Heine, Thiemo Mättig, and Jonas Kress.  \\

I am very thankful to have spent my university years with Charlie Kritschmar, with whom I experienced the joys of studying as well as the stressful times. She became a great friend and a very appreciated help whenever it comes to design. \\ 

Without the proof reading I would have been lost---therefore I want to express my sincere gratitude to, among others, Timo Krüger, Gerrit Schäfer, and Andrew Thomas Blake. \\

An open source project would not be the same without a community. I had the joy of working with and getting to know the communities of Wikidata and Wikipedia. I am very thankful for their input and interest in this project. \\

Last but not least I want to thank my family and friends for their everlasting love and support.