\documentclass[11pt]{article}
\title {{Non-functional requirements}}
\author {Lucie-Aim\'{e}e Kaffee}
\date{}

\begin {document}

  \section{Non-functional requirements}

  The extension is aiming to provide access to previously unavailable information. The requirements should all follow this main goal. \\
  User should be able to discover the Article Placholder generated pages while browsing the Wikipedia or researching a certain topic. \\
  While the content pages are auto-generated, editors of the different wiki projects should still feel a sense of ownership over the pages. They need to keep control over the articles as much as possible to adjust them to their own and their community's needs.  \\
  At the same time the extension should provide a default, that makes it attractive and engaging to use. Especially for speakers of the target languages- languages, that are under represented in the Wikipedia and have small communities and a small amount of articles. \\
  The pages should engage and encourage editing when appropriate. Therefore they should invite readers to create articles possibly with the information provided by Wikidata. They will need to have an option to translate existing articles from another language the reader may speak, too. \\
  The Wikipedia is a big and widely used project and has over the years built a reputation as a truth worthy source of knowledge. The extension should maintain and enhance this status. \\
  To not confuse readers and make clear what is happening the article placeholder must clearly differ form human-written articles. \\


  \begin{itemize}
    \item Providing access to to previously unavailable information --
    \item User should be able to discover the Article placeholder -- 
    \item Editors should feel sense of ownership \& control -- 
    \item Attractive and engaging to use (especially speakers of target languages) --
    \item invite Reader to create and/or translate article --
    \item Must maintain status of Wikipedia as a trust worthy source of knowledge --
    \item Clearly differs from a human-written article --
  \end{itemize}

\end {document}